A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-10-03 paper/paper.experiments.tex
Replace figures in experiments section

% JK: Good to introduce the detault parameters first, then for each parameter explored,
%     Describe what varied.
For the remaining experiments, we simulated a department with 10 clinicians offering 
two services, similar to the department at St.\ Michael's Hospital. 
Each clinician was
configured with $\{0, 5, 10, 15\}$ non-overlapping block
% JK: \abs{BR} does not clearly imply number of blocks (could be confused with week indices),
%     so just leave out the LHS here I think.
% JK: What do you mean by non-overlapping? And why only increments of 5?
requests.
The effect of an increasing number of requests per clinician on the runtime of
the ILP solver is shown in Figure~\ref{fig:runtime-requests}.
The increase in the number of requests did not affect the runtime of
the ILP solver, indicating that it can accommodate a lot of flexibility in
clinician requests. Moreover, we see that all four runs were completed in under
1 second.
% JK: See somments below about trends and repeating simulations.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.5]{fig/runtime_requests} % JK: can you export this to PDF or SVG to avoid pixelation?
	\caption{Runtime of ILP solver with an increasing number of requests per clinician}
  \label{fig:runtime-requests}
  % JK: The trend here is a bit confusing, since I think you're trying to say
  %     that the runtime is not affected by the number of constraints,
  %     but there is noise in these results.
  %     I would re-run this 10-100 times and average the results so that (I expect)
  %     the mean trend is actually flat. You could (should) then also present the runtimes
  %     as box-plots to show that the trend is less than the variability.
\end{figure}

% JK: Introduce what you did first and then the figure showing results (see above)
% JK: Try to introduce these results in the same order as they appear in the
%     first paragraph of this section.
Figure~\ref{fig:runtime-blocks} presents the change in runtime when increasing
the number of 2-week blocks $B = \{26, 52, 78, 104\}$ in a department with 10
clinicians offering two services. There does not seem to be a strong effect on
runtime when we lengthen the time-horizon of the schedule, and in fact the
solver was able to find an optimal schedule for all time horizons within 3
seconds. % 'very reasonable amount of time" is vague. what is reasonable?
%better to give a range in value.
% JK: same comment as above re. trends

\begin{figure}[h]
	\centering
	\includegraphics[scale=.5]{fig/runtime_blocks}
	\caption{Runtime of ILP solver with an increasing number of 2-week blocks}%
  \label{fig:runtime-blocks}
  % JK: same comment as above re. trends
  % JK: Thess figures could also possible be Figure 1. a) and b) 
\end{figure}

>>>>

% JK: Good to introduce the detault parameters first, then for each parameter explored,
%     Describe what varied.
For the remaining experiments, we simulated a department with 10 clinicians offering 
two services, similar to the department at St.\ Michael's Hospital. 
% JK: \abs{BR} does not clearly imply number of blocks (could be confused with week indices),
%     so just leave out the LHS here I think.
% JK: What do you mean by non-overlapping? And why only increments of 5?
The effect of an increasing number of requests per clinician on the runtime of
the ILP solver is shown in Figure~\ref{fig:runtime-requests}.
In this experiment, each clinician was configured with 1 to 15 total block requests.
The runtime of the algorithm is constant with respect to the number of requests,
indicating that it can accommodate a lot of flexibility in
clinician requests. Moreover, we see that all runs were completed in under
2 seconds.
% JK: See somments below about trends and repeating simulations.

\begin{figure}[h]
	\centering
	\def\svgwidth{\columnwidth}
	\caption{Runtime of ILP solver with an increasing number of requests per clinician}
	\input{fig/runtime-requests.pdf_tex} % JK: can you export this to PDF or SVG to avoid pixelation?
  \label{fig:runtime-requests}
  % JK: The trend here is a bit confusing, since I think you're trying to say
  %     that the runtime is not affected by the number of constraints,
  %     but there is noise in these results.
  %     I would re-run this 10-100 times and average the results so that (I expect)
  %     the mean trend is actually flat. You could (should) then also present the runtimes
  %     as box-plots to show that the trend is less than the variability.
\end{figure}

% JK: Introduce what you did first and then the figure showing results (see above)
% JK: Try to introduce these results in the same order as they appear in the
%     first paragraph of this section.
Figure~\ref{fig:runtime-blocks} presents the change in runtime when increasing
the number of 2-week blocks in a department with 10
clinicians offering two services. In this experiment, we investigated time horizons
from 5 to 110 blocks. This is equivalent to generating a schedule for up to 4 years ahead.
The trend in the graph indicates a linear growth in runtime with respect to the time-horizon.
Notably, the ILP solver was able to find all solutions in under 6 seconds, indicating very 
good performance for long-term scheduling. 
% 'very reasonable amount of time" is vague. what is reasonable?
%better to give a range in value.
% JK: same comment as above re. trends

\begin{figure}[h]
	\centering
	\def\svgwidth{\textwidth}
	\caption{Runtime of ILP solver with an increasing number of 2-week blocks}%
	\input{fig/runtime-blocks.pdf_tex}
  \label{fig:runtime-blocks}
  % JK: same comment as above re. trends
  % JK: Thess figures could also possible be Figure 1. a) and b) 
\end{figure}
